Variation in distance between consecutive animal locations

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
Test to use mpm only for 15 min intervals. Still get error if trying to use full distances instead of velocities

@@

@@

@@

>>>>

[@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle. 
*Would be interesting to add a figure with what I am actually analyzing. So, visually show how the gps locations get turned into straight lines, and angles, with an associated time interval. Or we could just multiply everything? So have it all for 15 minute intervals, and then repeat the ones that went on longer, perhaps set a limit for 60 minutes?*

@@

probabilistic rules of movement.

@@

aracari_df %>% 
  mutate(tmin = dt/60,
         mpm = dist/tmin) %>% 
  drop_na(tmin) %>% 
  filter(tmin == 15) %>% 
  group_by(id) %>% 
  tally() %>% 
  filter(n >=20)

@@

```{r}
focus <- "dist15"

df <- aracari_df %>%
  mutate(tmin = dt/60,
         mpm = dist/tmin,
         Bird_ID = paste0("B", id),
         focus = mpm) %>% 
  drop_na(tmin) %>% 
  filter(tmin == 15) %>% 
  dplyr::filter(dist != 0) %>% 
  group_by(id) %>%
  filter(., n() >= 20) %>%
  ungroup()

  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
  kpars <- c(1, 2, 2, 2, 2, 2, 2)
```
